---
title: "Chocolate Ratings (Kaggle)"
author: "Gregory Sorg"
date: "1/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction



```{r load libs and data}
library(tidyverse)
library(readr)
chocolate_makers <- read_csv("data/chocolate_makers.csv")
chocolate_ratings <- read_csv("data/chocolate_ratings.csv")
print(head(chocolate_makers))
print(head(chocolate_ratings))
```

Looks like a few columns will need altering/taken into account when analyzing:

  * '*Country of Bean Origin*': some beans are listed as from multiple countries or a blend (i.e. "*Sao Tome & Principe*")
  * '*Specific Bean Origin or Bar Name*` :  batch numbers, multiple descriptors
  * '*Cocoa Percent*':  percent sign should be removed
  * '*Ingredients*': should be divided into number then the letters designating the ingredients
  * '*Most Memorable Characteristics*':  Descriptors are separated by commas, with multiple characteristics per bar
  
Start by making a new column for number of ingredients, dummy values for each of the ingredients, and remove percent sign from *Cocoa Percent*:

```{r ingredient columns, warning=FALSE}
chocolate_ratings <- chocolate_ratings %>%
  mutate(NumberIngredients = map_chr(str_split(Ingredients, "-"),1),
         IngredientList = (str_split(Ingredients, "-")))%>%
  mutate(IngredientList = map(IngredientList, 2))%>%
  mutate(IngredientB = if_else(str_detect(IngredientList, "B"),1,0),
         IngredientS = if_else(str_detect(IngredientList, "S"),1,0),  #This will return 1 for Sa but there are no occurrences of Sa without also S
         IngredientC = if_else(str_detect(IngredientList, "C"),1,0),
         IngredientL = if_else(str_detect(IngredientList, "L"),1,0),
         IngredientV = if_else(str_detect(IngredientList, "V"),1,0),
         IngredientSa = if_else(str_detect(IngredientList, "Sa"),1,0))%>%
  mutate(CocoaPercent=as.numeric(str_sub(`Cocoa Percent`, 1,nchar(`Cocoa Percent`)-1)))


```

```{r}
unnest_test<- chocolate_ratings %>%
  mutate(`Most Memorable Characteristics`= str_split(`Most Memorable Characteristics`, ","))%>%
  unnest_wider(`Most Memorable Characteristics`)
library(fastDummies)
unnest_test_dum1<- unnest_test %>%
  dummy_cols(c("...1", "...2", "...3","...4", "...5"))

#step in right direction, need to eliminate the preceeding '...#' for dummy variables, then combine matching names




```

  
  
  